---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# stampr

<!-- badges: start -->
![stampr CRAN version](http://www.r-pkg.org/badges/version/stampr)
![stampr Age](https://rpkg.net/pub-age/stampr/blue)
[![stampr downloads](https://cranlogs.r-pkg.org/badges/last-month/stampr)](https://cran.r-project.org/package=stampr)
<!-- badges: end -->


The stampr package implments methods for spatial-temporal analysis of moving polygons (STAMP) which can be used to understand types of polygon changes and perform distance and directional analysis of polygon movement. The STAMP method is widely applicable in environmental applications and has been used to study animal home range and species distribution changes, the movement of objects such as forest fires and storm boundaries, and other dynamic features like dune formations. 

For more information on the methods used within read the documentation, but also consult the two papers that can be cited when using the package:

Robertson, C., Nelson, T.A., Boots, B., Wulder, M.A. (2007) STAMP: Spatial-temporal analysis of moving polygons. Journal of Geographical Systems. 9:207-227. [Article Link](https://doi.org/10.1007/s10109-007-0044-2)

Long, J., Robertson, C., Nelson, T. (2018). stampr: Spatial-Temporal Analysis of Moving Polygons in R. Journal of Statistical Software, Code Snippets, 84(1), [article link](https://doi.org/10.18637/jss.v084.c01)

## Installation

You can install the latest (under development version) of stampr from github:

```{r gh-installation, eval = FALSE, message = FALSE, warning = FALSE}
devtools::install_github("jedalong/stampr")
```

To download the latest version from CRAN: 

```{r eval=FALSE}
install.packages('stampr')
```

--- END --- 